---
title       : What would be your destiny if you were Titanic passenger?
subtitle    : 
author      : Anastasiia
job         : 
framework   : io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [bootstrap, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        :



---

## Main Question


Imagine, that you are the Titanic passenger.

Did you have a chance for surviving?



<h2>Lets see !</h2>


---

## How to answer this question?

We comparing your data(age and sex) and our prediction. 





<h2> What is "our prediction"? </h2>

Machine Learning model based on real passenger surviving.

<h2> What is the data? </h2>

It is subset from Kaggle competition "Titanic: Machine Learning from Disaster"
You could find it here http://www.kaggle.com/c/titanic-gettingStarted.

The subset contains variables "age", "sex", "survived" and include 714 rows.



---


## How we made this prediction?
We trained a model using randomForest algorithm with ntree=50.

Suppose, your age is 30 and you sex is male.
Did you have a chance?

```{r echo=F, results="axis"}
surviving_prob <- function(age, sex){
  tree_mod <- randomForest(survived ~ ., data=titanic, ntree=50)  
  new_data <- data.frame(age=age, sex=sex)
  new_data$sex <- factor(new_data$sex , levels = c("female", "male"))
  prediction <- predict(tree_mod, new_data)
  return(prediction)
}

titanic <- read.csv("cutted_titanic.csv")
titanic$survived[titanic$survived == 0] <- 'No'
titanic$survived[titanic$survived == 1] <- 'Yes'
titanic$survived <- as.factor(titanic$survived)
as.character(surviving_prob(30, "male"))

```

```{r echo = F, results = 'asis'}
require(ggplot2)
titanic <- read.csv("cutted_titanic.csv")
titanic$survived[titanic$survived == 0] <- 'No'
titanic$survived[titanic$survived == 1] <- 'Yes'
titanic$survived <- as.factor(titanic$survived)

    p <- ggplot(titanic, aes(age, sex, color=survived))+
    geom_point(pch = 19) +
    geom_point(aes(30, "male"), color="black", cex=10, pch=4) +
    geom_text(aes(40, "male"), color="darkblue", label="You")

    p

```



---

## How good is our prediction?

```{r echo = T}
require(randomForest)
tree_mod <- randomForest(survived ~ ., data=titanic, ntree=50)
tree_mod

```

